Practical Concurrent Priority Queues \\ Student Paper for Seminar in Algorithms 2013W \\ Technical University of Vienna

### 2014-04-04 paper/paper.Rnw
Remove TODOs that are really WONTDOs

SkipLists \cite{pugh1990skip} have become increasingly popular in concurrent data structures because 
they are both simple to implement, and exhibit excellent disjoint-access parallelism. In contrast to
search trees and Heaps, reorganization is not necessary, since SkipLists rely on
randomization for an expected $O(\log n)$ complexity of \lstinline|Insert|, \lstinline|Search|
and \lstinline|Delete| operations.
A SkipList may be visualized as a set of linked lists with corresponding levels. The linked
list at level 0 is the sorted sequence of all objects in the SkipList,
and higher levels provide ``shortcuts''
into the SkipList such that a list of level $i + 1$ contains a subset of the objects in level
$i$. A SkipList node $n$ is said to be of level $i$ if it is in all lists of levels $[0, i]$
and in none of levels $[i + 1, \infty]$. Upon insertion, the new node's level is assigned at random
according to a geometric distribution; deletion simply removes the node.

% TODO: Maybe integrate into description - otherwise remove. Do we need further detail?

@@

% TODO: This counts for all skiplist impls.

@@

% TODO: Linearizability points.

@@

% TODO: Mention backoff.

@@

% TODO: Further details?

@@

In each test run, the examined priority queue was initially filled with $2^{15}$
elements. We then ran a tight loop of $50\%$ insertions and $50\%$ deletions
for a total of $10$ seconds, where all \lstinline|Insert|
operations within this context implicitly choose a key uniformly at random from
the range of all 32-bit integers. This methodology seems to be the de facto standard for concurrent % TODO: Similar phrasing as linden :(
priority queue benchmarks
\cite{alistarhspraylist,linden2013skiplist,shavit2000skiplist,sundell2003fast}.
Each run was repeated for a total of $10$ times
and we report on the average throughput.

>>>>

SkipLists \cite{pugh1990skip} have become increasingly popular in concurrent data structures because 
they are both simple to implement, and exhibit excellent disjoint-access parallelism. In contrast to
search trees and Heaps, reorganization is not necessary since SkipLists rely on
randomization for an expected $O(\log n)$ complexity of \lstinline|Insert|, \lstinline|Search|
and \lstinline|Delete| operations.
A SkipList may be visualized as a set of linked lists with corresponding levels. The linked
list at level 0 is the sorted sequence of all objects in the SkipList,
and higher levels provide ``shortcuts''
into the SkipList such that a list of level $i + 1$ contains a subset of the objects in level
$i$. A SkipList node $n$ is said to be of level $i$ if it is in all lists of levels $[0, i]$
and in none of levels $[i + 1, \infty]$. Upon insertion, the new node's level is assigned at random
according to a geometric distribution; deletion simply removes the node.

@@

@@

@@

@@

@@

In each test run, the examined priority queue was initially filled with $2^{15}$
elements. We then ran a tight loop of $50\%$ insertions and $50\%$ deletions
for a total of $10$ seconds, where all \lstinline|Insert|
operations within this context implicitly choose a key uniformly at random from
the range of all 32-bit integers. This methodology seems to be the de facto standard for concurrent
priority queue benchmarks
\cite{alistarhspraylist,linden2013skiplist,shavit2000skiplist,sundell2003fast}.
Each run was repeated for a total of $10$ times
and we report on the average throughput.
